Predicting Donald Trump's win

### 2020-11-02 outputs/paper/paper.Rmd
edit equations in model

\begin{align}log(\frac{p}{1-p})= B_0 + B_1x_1 + B_1x_2 + B_1x_3 + B_1y_1 + B_1y_2 + B_1y_3\end{align}

Where *p* is the probability that the event of interest occurring (voting for Joe Biden), $B_0$ is the y-intercept and $B_i, 1\leq i\leq k,$ coefficient represents change in log odds for one unit increase in $x_i$.

>>>>

\begin{align}log(\frac{p}{1-p})= B_0 + B_1x_1 + B_2x_2 + B_2x_3 + B_4y_1 + B_5y_2 + B_6y_3\end{align}

Where *p* is the probability that the event of interest occurring (voting for Joe Biden), $B_0$ is the intercept and $B_i, 1\leq i\leq 6,$ coefficient represents change in log odds for one unit increase in $x_j$ or $y_j, 1\leq j\leq 3$.
